---
title: The games I played in 2018 Part Two - Insights
author: Will Bidstrup
date: '2018-12-30'
slug: the-games-i-played-in-2018-part-two-insights
categories:
  - R
tags:
  - R
  - visualisation
---

In a previous post I explored my gaming data from 2018.  

Today I'm going to zero in on only 2018 data with two objectives;  

1. Find five interesting things  
2. Visualise those things  

Because data exploration and visualisation is such a black hole I'm going to limit myself to **one hour** to achieve these objectives.  


```{r, message = FALSE}
library(jsonlite) # To read in the .json format which is default export from BG Stats
library(here) # For relative file paths
library(tidyverse)  # For general wrangling and exploration  
library(padr) # To fill in or 'pad' dates in a date series  
```


# Import

```{r}
# Read json from BG Stats export
d <- fromJSON("data/BGStatsExport.json")

```

```{r}
# Extract into data frames
games <- data.frame(d[3])
plays <- data.frame(d[4])
locations <- data.frame(d[5])
players <- data.frame(d[6])
```

# Pre-process

I create plays_plus which is the plays information enhanced with information about the games.  

```{r}
# Create plays_plus, an enhanced data frame with elements from games.  

## Create game ID lookup  
game_id_lookup <- games %>%
  select(games.id, games.name)

## Join to plays
plays_plus <- plays %>%
  left_join(game_id_lookup, by = c("plays.gameRefId" = "games.id"))
```

```{r}
time_per_game <- plays_plus %>%
  group_by(games.name) %>%
  summarise(total_mins = sum(plays.durationMin, na.rm = T),
            total_hours = round(total_mins /60, digits = 2))
```

```{r}
plays_plus <- separate(plays_plus, col = plays.playDate, into = c("date","time"), sep = " ")

plays_plus$date <- as.Date(plays_plus$date, format = "%Y-%m-%d")
```

```{r}
# TODO - figure out grepl in ifelse for iPad
# Categorise games
plays_plus$game_type <- ifelse(plays_plus$games.name %in% c("Dungeons & Dragons 5E", "Tales From The Loop", "Conan: Adventures In An Age Undreamed Of"), "RPG",
                               ifelse(plays_plus$games.name %in% c("Stardew Valley (iPad)", "Don’t Starve (iPad)", "Six Ages: Ride Like The Wind (iPad)", "Baldur’s Gate (iPad)"), "iPad","Other"))


```


I create a summary of the year by padding in all the days I didn't play.  

```{r}
year_summary <- plays_plus %>%
  pad %>%
  group_by(date, games.name) %>%
  summarise(total_mins = sum(plays.durationMin, na.rm = T),
            total_hours = round(total_mins /60, digits = 2)) 



year_summary$cum_hours <- cumsum(year_summary$total_hours)
```


# Insights

## How much time did I spend playing games?  


```{r}
ggplot(data = year_summary %>%
         filter(date > "2017-12-31"), aes(x = date, y = cum_hours)) +
  geom_line() +
  theme_minimal() +
  labs(title = "Cumulative gaming time in 2018",
       x = "Date",
       y = "Cumulative hours")
```


## What games did I play the most?  


