---
title: Finding a house to rent with R
author: Will Bidstrup
date: '2018-12-25'
slug: finding-a-house-to-rent-with-r
categories:
  - R
tags:
  - R
---

I find myself in a real world situation where web scraping will be useful. I've never tried it before, this will be my first go at getting something happening.  

My objective is to collect information from [realestate.com.au](https://www.realestate.com.au/rent/) to help me understand the market before moving to Adelaide.  

I'll be using the 'rvest' package and hacking my way through while reffining to a couple of tutorials [here](https://www.analyticsvidhya.com/blog/2017/03/beginners-guide-on-web-scraping-in-r-using-rvest-with-hands-on-knowledge/) and [here](https://www.datacamp.com/community/tutorials/r-web-scraping-rvest).  

```{r, include = FALSE}
install.packages("rvest", repos="http://cran.rstudio.com/")

```


```{r, message = FALSE}
library(tidyverse) # For everything
library(rvest) # For some prettier themes
```


# Scraping a single page

I start with a simple rental search for properties between 300 and 450 per week with minumum 3 bedrooms.  

```{r}
url <- "https://www.realestate.com.au/rent/property-unitblock-villa-townhouse-unit+apartment-house-with-3-bedrooms-between-300-450-in-adelaide,+sa+5000/list-1"
```


```{r}
webpage <- read_html(url)
```

I will start with weekly Price which is defined as .priceText

```{r}
price_data_html <- html_nodes(webpage,'.priceText')

price_data <- html_text(price_data_html)

head(price_data)
```

Then the number of bedrooms, bathrooms and carspaces which is simply dd


```{r}
beds_data_html <- html_nodes(webpage,'dd')

beds_data <- html_text(beds_data_html)

head(beds_data)
```


# Refining the elements




# Running the scraping over all items